\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
o f -> of
malformed sentence + reword (pypi)
avoid "comprises of"

This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}. The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. \PYGEOMETRY{} allow the rapid creation and 
adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}. This paper describes version 1.0 o f \PYGEOMETRY{}, which is freely available as a git repository and via PyPi.package manager.

@@

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and 
neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC \cite{DAGMC} and McCAD \cite{McCad}.  
In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model comprises of a large number of parts. Exporting, assigning material to and placing the STL components into the RTMC can be a cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.

>>>>

This paper describes a geometry creation and conversion package called \PYGEOMETRY{}, written in Python and internally based on the Geant4 application programming interface (API) and the Geometry Description Markup Language (GDML) for file persistency  \cite{GDML}. The main features of \PYGEOMETRY{} are a Python scripting API to rapidly design parametrised geometry; conversion to and from  FLUKA geometry descriptions; conversion from CAD formats  (STEP and IGES) based on FreeCAD \cite{FreeCAD} and OpenCascade \cite{OpenCASCADE}; and powerful geometry visualisation tools based on VTK \cite{VTK4}. The origin of \PYGEOMETRY{} was a set of utilities to prepare geometry for an accelerator beamline simulation program based on Geant4 called BDSIM \cite{BDSIM_Nevay}. Accelerator physicists, like specialists in other areas, need a tool to quickly model specialist geometry and the subsequent interaction of the charged particle beam. \PYGEOMETRY{} allow the rapid creation and 
adaptation of geometry. Figure~\ref{fig:workflow} depicts various workflows possible with \PYGEOMETRY{}. \PYGEOMETRY{} is not an executable software package but a toolkit, a user would typically write a very small Python program to use to use the classes and functions provided by \PYGEOMETRY{}. This paper describes version 1.0 of \PYGEOMETRY{}, which is freely available as a git repository and via the Python Package Index (PyPi).

@@

There are existing codes that have functionality similar to \PYGEOMETRY{}. ROOT \cite{Brun:1997pa}, the high-energy physics data analysis program, can load, display and manipulate GDML-like geometry. Tools exist to convert CAD files to GDML, open source examples are GUIMesh \cite{GUIMesh_Pinto}, commercial products include ESABASE2 \cite{ESABASE2} and FASTRAD \cite{FASTRAD}. There are also tools from the fusion and 
neutronics community that can convert CAD geometry into formats usable by RTMC codes examples include DAGMC \cite{DAGMC} and McCAD \cite{McCad}.  
In principle CAD software can export shape data to STL (or other similar mesh formats), which can be used by Geant4 \cite{poole2012acad}. In practice, using a lot of CAD models is difficult if a CAD model is comprised of a large number of parts. Exporting, assigning material to and placing the STL components into the RTMC can be a cumbersome task. The existent set of software does not provide a complete set of tools to efficiently create complex geometries.
